Syntactic realization with data-driven neural tree grammars

### 2016-10-10 paper/draft.tex
for the merge

Using the representations of \ref{sec:neural}, the models of
\ref{sec:models} can be instantiated in six different ways.  We can
use a feed-forward Fergus-N architecture or a recurrent Fergus-R
architecture.  Each architecture can embed supertags \emph{minimally},
by a simple one-hot vector; \emph{atomically}, by learning an
embedding vector corresponding to each supertag; or
\emph{structureally}, by using a convolutional coding over the
supertag tree structure.

@@

From this input, we extracted the atomic supertag prediction instances
and trained a network defined by each of the architectures of
\ref{sec:models} and each of the supertag representations of
\ref{sec:neural}.  As always, we used Section XXX for development,
Sections XXX for training, and Section XXX for testing.  A complete
description of network organization and training parameters is given
in the appendix.  Our code is available XXX.

@@

Next, we evaluate the models on the full NLG task, including
linearization.  
%
The linearization tasks licenses more freedom in supertag
classifications because it may have the same root and leaf syntactic
categories but differ in minor constructions, such as number of
arguments.
%
The freedom allows for models to be more generalized and less fit to
the specific supertags, but at the same time, it also mutes the
distinctions between classification decisions.
%
We report XXXMEASURE, following \cite{}.
%
They argue that their measure correlates with NLG performance better
than n-gram counting methods.
%
Since linearization uses a beam search, we report statistics both for
the top-ranked beam and for the empirically based beam among the
candidates computed during search.
%
The difference gives an indication of the effect of the language model
in guiding the decisions that remain after supertagging.

>>>>

Using the representations of \ref{sec:neural}, the models of
\ref{sec:models} can be instantiated in six different ways.  We can
use a feed-forward Fergus-N architecture or a recurrent Fergus-R
architecture.  Each architecture can embed supertags \emph{minimally},
by learning a scalar corresponding to each supertag; \emph{atomically}, by learning an
embedding vector corresponding to each supertag; or
\emph{structureally}, by using convolutional coding over each
supertag's tree structure.

@@

From this input, we extracted the atomic supertag prediction instances
and trained a network defined by each of the architectures of
\ref{sec:models} and each of the supertag representations of
\ref{sec:neural}.  As always, we used Section 02-21 for development,
Sections 22 for training, and Section 23 for testing.  A complete
description of network organization and training parameters is given
in the appendix.  The code and complete experimental setup are publically available\footnote{https://github.com/braingineer/neural\_tree\_grammar}.

@@

Next, we evaluate the models on the full NLG task, including
linearization.  
%
The linearization tasks licenses more freedom in supertag
classifications because it may have the same root and leaf syntactic
categories but differ in minor constructions, such as number of
arguments.
%
The freedom allows for models to be more generalized and less fit to
the specific supertags, but at the same time, it also mutes the
distinctions between classification decisions.
%
We report a modified edit distance measure, Generation String Accuracy, following \cite{bangalore2000evaluation}.
%
They argue that their measure correlates with NLG performance better
than n-gram counting methods.
%
Since linearization uses a beam search, we report statistics both for
the top-ranked beam and for the empirically based beam among the
candidates computed during search.
%
The difference gives an indication of the effect of the language model
in guiding the decisions that remain after supertagging.
